---
title: "Vignette: Create boilerplatePackage"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette: Create boilerplatePackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(jeksterslabRpkg)
```

## Create a Boilerplate `R` Package.

Creates a boilerplate `R` package by generating the following:

  - `DESCRIPTION` file,
  - `NAMESPACE` file,
  - `LICENSE` and `LICENSE.md`,
  - a simple `R` script and accompanying `Rd` documentation file,
  - sample data, test, and vignette,
  - optional `pkgdown` and `travis` `YAML` files,
  - optional `README.Rmd` file, and
  - other files like `.Rbuildignore`, `.gitignore`, and `Rproj`.

Optionally, the function can also set up a `Git` repository
and push the created repo to `Github`.
This requires that `git` and `hub` are installed
and configured in the system.

If you are going to document, check, and build your package using `devtools`,
you may delete the boilerplate `NAMESPACE` and `MAN` files.

```{r create_01, eval = FALSE}
pkg_create(
  pkg_dir = getwd(),
  input_file = "DESCRIPTION.yml",
  docs = TRUE,
  pkgdown = TRUE,
  travis = TRUE,
  appveyor = TRUE,
  readme = TRUE,
  add_description = NULL,
  add_namespace = NULL,
  add_rbuildignore = NULL,
  add_gitignore = NULL,
  add_travis = NULL,
  add_appveyor = NULL,
  git = TRUE,
  github = TRUE
)
```
